Interpolation and extrapolation-based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel

### 2023-01-23 Article.tex
order of authors
new modifications

% specify here the journal
\journal{International Journal of Mechanical Sciences}

@@

\author[LGP]{Pierre Tize Mha}
\author[ETS]{Prashant Dhondapure}
\author[LGP]{Amèvi Tongne}
\author[ETS]{Mohammad Jahazi}
\author[LGP]{Olivier Pantalé\corref{cor1}}
\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads \cite{tian2022deformation, tavakoli2019ferrite}.
It has also been reported that phase transformation can occur during deformation.
The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, Ashtiani-2012, He-2013, Changizian-2012}.

Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed.
Among these, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes.
Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}.
However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}.
To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
However, in the PTM model, the high order of the polynomial function (up-to $10$ in some cases) can affect its accuracy.

The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$}
\label{fig:RawData}
\end{figure}
All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21,000$ data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$, but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, and then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}.
The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
The increase of stress observed at the beginning of the deformation and up-to $0.1$ is due to work hardening (WH).
After $0.1$ and up-to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work-hardening rate.
This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$, except for those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and a $0.1$ $\text{s}^{-1}$ strain rate; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels.
In fact, the drop observed in
stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.

@@

The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon$, strain rate $\mdot\varepsilon$, and temperature $T$.
However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
The equation that describes this model is given as follows \cite{Johnson-1983}:
\begin{equation}
\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
\end{equation}
where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$, respectively.

The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{He-2013}.
This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering only all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the previously identified parameters and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.

@@

The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the Mean Absolute Relative Error ($\MARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
Therefore, as a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we avoided its use in our analysis.

@@

The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEM codes such as the Abaqus software.
The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously, and for that formulation, MZA is preferred to the JC model \cite{Hull-2011}.
However, the original form of the ZA model has some limitations due to the fact that it is considered as a two terms function (thermal and athermal functions), and to improve the formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right],
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009}, and the parameters are summarized in Table \ref{tab:MZA}, while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
\begin{table}[h!]
\centering{}
\caption{Parameter constants of Modified Zerilli-Armstrong model}
\begin{tabular}{ccccccc}
	\hline
	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
\end{tabular}
\label{tab:MZA}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental flow stresses and those predicted by the MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}
It can be seen from this figure that the MZA model as well as the JC model is not able to faithfully reproduce the experimental data at low strain rates, but is much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.

@@

The Hansel-Spittel model \cite{Hensel-1978} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
Programming a simple identification script is sufficient to identify its parameters for a given material.
The equation of the HS model is given by the following relation:
\begin{equation}
\sigma^y = A~\e{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~\e{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~\e{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}, \label{eq:HS}
\end{equation}
where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature, as proposed earlier.
The coefficients $A$ and $m_i$ are the 9 parameters of the model to be identified.
However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
For its identification, several authors restrict its expression to a reduced number of only $5$ or $6$ $m_i$ parameters, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.

@@

Because of their predictive capacity and adaptability, Artificial Neural Networks (ANNs) are increasingly widely used today in many scientific fields.
Their operation is based on a learning process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine learning process.

Neural networks generally have two uses: classification and regression.
The first is the ability to classify data into different groups, and for example, to distinguish between images of cats and dogs.
The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after learning, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the previously identified analytical models.
The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
A feed-forward ANN, as used in our application, contains an input layer, an output layer and a number of hidden layers ($2$ in our case).
Each layer of neurons is connected to the one before it and the one after it by weighted connections.
Thus, all the neurons of the $k$ layer are connected to all the neurons of the ($k-1$) layer as shown in Figure \ref{fig:ANN-2HL}.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Multi-layer Artificial Neural Network architecture}
\label{fig:ANN-2HL}
\end{figure}

>>>>

% specify here the journal
\journal{Materials \& Design}

@@

\author[LGP]{Pierre Tize Mha}
\author[ETS]{Prashant Dhondapure}
\author[LGP]{Olivier Pantalé\corref{cor1}}
\author[ETS]{Mohammad Jahazi}
\author[LGP]{Amèvi Tongne}
\ead{Olivier.Pantale@enit.fr}
\ead[url]{http://www.enit.fr}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in the automotive industry as dies for the production of bumpers and dashboards through the plastic injection process.
The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and a quench and temper heat treatment process to achieve the desired mechanical properties \cite{chadha2017deformation, chadha2018influence, murugesan2019two}.
In recent years, in order to respond to the market demand, larger size forgings have had to be produced.
In parallel, more stringent conditions related to chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block have been required.
Of the three manufacturing steps (casting, forging and heat treatment), forging is where the most important microstructural changes take place, and which greatly influences the final properties that can be achieved \cite{murugesan2019hybrid, chadha2020microstructure, sripada2022effect}.
The open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, take place concomitantly with softening phenomena such as recovery and recrystallization under static and/or dynamic thermomechanical loads \cite{tian2022deformation, tavakoli2019ferrite}.
It has also been reported that phase transformation can occur during deformation.
The extent and intensity of the above phenomena strongly depend on three macroscopic quantities, namely, the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ \cite{ebrahimi2017flow, shi2022constitutive, zeng2022constitutive, rudra2019constitutive}.

Considering the large size of blocks, a purely experimental approach, based on trial and error, can not be used by industry, and therefore, reliable predictive tools, such a Finite Element analysis (FEA) codes, have been developed, and are commercially available.
However, the prediction reliability of such analyses is a function of the accuracy of the material constitutive model, which describes the mutual interactions between the strain, the strain rate, and the temperature during deformation.
As mentioned above, precipitation and phase changes are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides.
Hence, most constitutive models depend on macroscopic parameters which influence the hardening and softening of the material.
A large number of phenomenological, semi-empirical, or physical models \cite{jia2022thermo, costa2016study, rudnytskyj2020constitutive, Pantale-2021} have been developed.
Among these, the Johnson-Cook (JC) \cite{jia2021modified}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{sim2022modified} models are the best known and most widely available in FEA codes.
Despite their simplicity, each of them suffers from certain shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from a lack of non-coupling between the strain, the strain rate and the temperature, while the HS model is better adapted for higher strain rate conditions \cite{chadha2018approach}.
To circumvent these shortcomings, several modified model forms have been developed \cite{chadha2018approach, liu2021modified, jia2022thermo1, bai2022comparison, zhu2022constitutive}.
However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, cannot be accurately predicted, and none of the models is able to accurately predict the flow behavior outside the experimental testing interval that was used to determine the model constants.
Due to its more physics-based formulation, the ZA model and its modified form, MZA \cite{ovesy2020explicit, niu2020constitutive, Muralli-2017, Cheng-2021, Muralli-2021}, and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{derazkola2021review, wang2022deformation, miao2022deformation}.
The Arrhenius formulation has been revised repeatedly to achieve a more accurate determination of the activation energy for high temperature deformation \cite{rudnytskyj2022investigating, ji2020optimization}.
To overcome the strong dependency of the models on specific alloy types, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type.
This formulation is based on the MZA model and the polynomial functions of undefined order that are used during the identification.
However, in the PTM model, the high order of the polynomial function (up-to $10$ in some cases) can affect its accuracy.

The Artificial Neural Network (ANN) is an approach used to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law.
It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model.
Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors which are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited.
Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships.
Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{wu2022experimental, stoffel2020deep, Ashtiani-2016-CSP, Stoffel-2019-NNB}.
Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software, as reported by Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
In fact, the implementation of a constitutive model in an FEA code requires the derivatives of the model with respect to strain, strain rate and temperature.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$}
\label{fig:RawData}
\end{figure}
All data curves contain $700$ equidistant strain values up-to $\varepsilon=0.7$.
Therefore, there are $6$ strain rates and $5$ temperatures, and the database consists of $21,000$ data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$, but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, and then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{galos2022review}.
The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time, and friction thus increases.
The increase of stress observed at the beginning of the deformation and up-to $0.1$ is due to work hardening (WH).
After $0.1$ and up-to $0.2$, the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of the work-hardening rate.
This behavior indicates that thermal softening becomes more and more predominant until it exceeds WH.
At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening.
This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$, except for those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and a $0.1$ $\text{s}^{-1}$ strain rate; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$).
Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates.
In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels.
In fact, the drop observed in
stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$.

@@

The JC model, as mentioned above, is one of the most widely used analytical models because it can be applied to many materials under different conditions of strain $\varepsilon$, strain rate $\mdot\varepsilon$, and temperature $T$.
However, the formulation of this model does not take into account the simultaneous effect of strain, strain rate and temperature.
Indeed, it is formulated by describing the effect of each physical parameter ($\varepsilon$, $\mdot\varepsilon$ and $T$) separately as a factor in the mathematical expression of the model, hence its inability to describe the phenomenon of softening induced by temperature.
The equation that describes this model is given as follows \cite{jia2021modified}:
\begin{equation}
\sigma^y=\left(A+B\varepsilon^{p^{n}}\right) \left[1+C\ln\left(\frac{\mdot\varepsilon}{\mdot\varepsilon_0}\right)\right] \left[1-\left(\frac{T-T_0}{T_m-T_0}\right)^{m}\right],\label{eq:Johnson-Cook}
\end{equation}
where $\sigma^y$ is the flow stress, $\varepsilon^p$ is the plastic strain, $A$ is the initial elastic limit of the material, $B$ is the strain hardening coefficient, $n$ is the strain hardening exponent, $C$ and $m$ are the material constants that describe the strain rate hardening coefficient and the thermal softening coefficient, respectively.
The other values are reference values: $\mdot\varepsilon_0$ is the reference strain rate, $T_m$ and thus $T_0$ are the melting temperature ($1460\celsius$ in our case) and the reference temperature, respectively.
For the determination of the parameters of the analytical models, the reference values for strain rate and temperature are $\mdot\varepsilon_0=0.001~\ps$ and $T_0=1050\celsius$, respectively.

The procedure used to determine the parameters of the Johnson-Cook law is in accordance with the one proposed by He \eal \cite{zeng2022constitutive}.
This method allows sequentially obtaining the $5$ parameters in the order $A$, $B$, $n$, $C$ and $m$.
Thus, according to the experimental data, the initial elastic limit of the material at the reference strain rate $\mdot\varepsilon_0$ and the reference temperature $T_0$ is $A=13.5143~\MPa$.
For the determination of the constants $B$ and $n$, from the results of the compression test at $T_0$ and $\mdot\varepsilon_0$, these two constants can then be determined by considering only the first term $\left(A+B\varepsilon^{p^{n}}\right)$ in Equation (\ref{eq:Johnson-Cook}).
Thus, here, $B=21.816~\MPa$ and $n=0.0746$.
Once the parameters $A$, $B$ and $n$ are known, the determination of $C$, considering only all the curves at $T=T_0$ then gives $C=0.3404$.
Finally, the last parameter $m$ is identified from the curves at $\mdot\varepsilon=\mdot\varepsilon_0$ and from knowledge of the parameters $A, B, C, n$ and gives $m=0.7057$.
All parameters of the Johnson-Cook model are reported in Table \ref{tab:JC}.

@@

The accuracy and predictive ability of the models are usually assessed through certain coefficients such as the Mean Absolute Relative Error ($\MARE$) defined by Equation (\ref{eq:AARE}):
\begin{equation}
\MARE(\%) = \frac{1}{N} \sum_{i=1}^{N}{\left|\frac{\sigma_i^p -\sigma_i^e}{\sigma_i^e}\right|} \times 100, \label{eq:AARE}
\end{equation}
and the Root Mean Square Error ($\RMSE$) defined by Equation (\ref{eq:RMSE}):
\begin{equation}
\RMSE (\MPa) = \sqrt{\frac{1}{N} \sum_{i=1}^{N} \left(\sigma_i^p - \sigma_i^e\right)^2}, \label{eq:RMSE}
\end{equation}
where $\sigma_i^e$ is the experimental value, $\sigma_i^p$ is the value predicted using the given model of the flow stress $\sigma^y$ and $N$ is the total number of data points used to compute those coefficients (in our case $N=21~000$).
For the JC model, $\MARE=14.05~\%$ and $\RMSE=12.00~\MPa$.
As reported by Phaniraj \cite{Phaniraj-2003},  the correlation coefficient ($\R$) is not always an accurate measure to evaluate the reliability of the constitutive law espacially in the case of a highly non-linear functions because it only shows the correlation of the model with respect to the data and not its accuracy. Therefore, a good (high) value of $\R$ (close to $1$) does not necessarily mean a good prediction of the model, but simply establishes a good linearity correlation between the experiment and the prediction, we avoided its use in our analysis.

@@

The MZA model, which is the modified form of the ZA model, like the JC model presented earlier, is one of the most widely used models implemented in many FEM codes such as the Abaqus software.
The difference between the MZA model and JC model is related to the consideration of the three physical parameters to describe the reality observed from experiments.
In the JC model, the parameters are considered separately, while in MZA, they are considered simultaneously, and for that formulation, MZA is preferred to the JC model \cite{zhu2022thermal}.
However, the original form of the ZA model has some limitations due to the fact that it is considered as a two terms function (thermal and athermal functions), and to improve the formulation, Samantaray \eal \cite{Samantaray-2009} proposed a modified form given by the following equation:
\begin{equation}
\label{eq:MZA-model}
\sigma^y = \left(C_{1}+C_{2}\varepsilon^{p^n}\right) \exp\left[-\left(C_{3}+C_{4}\varepsilon^p\right)\left(T-T_0\right) + \left(C_{5}+C_{6}\left(T-T_0\right)\right)\ln\left( \frac{\mdot\varepsilon}{\mdot{\varepsilon}_0}\right)\right],
\end{equation}
where the $7$ coefficients $C_i$ and $n$ are the parameters of the model to be identified for a given material.
To get the parameters of the MZA model, we apply the method proposed by \cite{Samantaray-2009}, and the parameters are summarized in Table \ref{tab:MZA}, while their predictions are plotted in Figure \ref{fig:CompExp-MZA-6}.
\begin{table}[h!]
\centering{}
\caption{Parameter constants of Modified Zerilli-Armstrong model}
\begin{tabular}{ccccccc}
	\hline
	  $C_1$   &   $C_2$   &         $C_3$          &         $C_4$          &  $C_5$   &         $C_6$         &   $n$    \\
	$13.5143$ & $21.2591$ & $4.7902\times 10^{-3}$ & $1.4895\times 10^{-4}$ & $0.1389$ & $1.495\times 10^{-4}$ & $0.0621$ \\ \hline
\end{tabular}
\label{tab:MZA}
\end{table}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/CompExp-MZA-6}
\caption{Comparison between the experimental flow stresses and those predicted by the MZA model}
\label{fig:CompExp-MZA-6}
\end{figure}
It can be seen from this figure that the MZA model as well as the JC model is not able to faithfully reproduce the experimental data at low strain rates, but is much better for high strain rates.
The deviation between the predicted values and the experimental values is large because this model has a problem correctly describing the softening in its formulation.
For the MZA model, $\MARE=21.20~\%$ and $\RMSE=19.57~\MPa$, showing an overall worse performance than the JC model, as reported in \cite{TizeMha-2022}.

@@

The Hansel-Spittel model \cite{savaedi2022review} is one of the least known models in terms of integration in FEM codes, although its parameters can more easily be determined than those of the JC or MZA models.
Programming a simple identification script is sufficient to identify its parameters for a given material.
The equation of the HS model is given by the following relation:
\begin{equation}
\sigma^y = A~\e{m_1T}~\varepsilon^{m_2}~\mdot\varepsilon^{m_3}~\e{({m_4}/{\varepsilon})}~(1+\varepsilon)^{m_5T}~\e{m_6\varepsilon}~\mdot\varepsilon^{m_7T}~T^{m_8}, \label{eq:HS}
\end{equation}
where again, $\sigma^y$ is the flow stress, $\varepsilon$ is the strain, $\mdot\varepsilon$ is the strain rate and $T$ is the temperature, as proposed earlier.
The coefficients $A$ and $m_i$ are the 9 parameters of the model to be identified.
However, this model has some shortcomings, notably related to the fact that its accuracy varies according to the number of parameters taken into account during the identification.
For its identification, several authors restrict its expression to a reduced number of only $5$ or $6$ $m_i$ parameters, by forcing a zero value for the other parameters \cite{Chadha-2018, Mehtedi-2015, Rudnytskyj-2020}.

@@

Because of their predictive capacity and adaptability, Artificial Neural Networks (ANNs) are increasingly widely used today in many scientific fields.
Their operation is based on a training process during which the principle of minimizing the error between the model's output and the training data allows the adjustment of the model's parameters, as in any machine training process.

Neural networks generally have two uses: classification and regression.
The first is the ability to classify data into different groups, and for example, to distinguish between images of cats and dogs.
The second corresponds to the universal approximation capacity of these neural networks, which is of interest to us herein, and thus, to the ability, after training, to predict the flow stress $\sigma^y$ values according to the input data, akin to what is done by the above identified analytical models. 
The main difference is that this approximation is not linked to a fixed mathematical formulation (as in JC, MZA, AR, HS and PTM analytical models), but is only dependent on the data used for training, the number of layers, the number of neurons per layer, and the activation functions associated with the neurons of the network.
A feed-forward ANN, as used in our application, contains an input layer, an output layer and a number of hidden layers ($2$ in our case).
Each layer of neurons is connected to the one before it and the one after it by weighted connections.
Thus, all the neurons of the $k$ layer are connected to all the neurons of the ($k-1$) layer as shown in Figure \ref{fig:ANN-2HL}.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Multi-layer Artificial Neural Network architecture}
\label{fig:ANN-2HL}
\end{figure}
